Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2024-08-17 analysis/paper/Letter_Response_to_Reviewers.qmd

Dr. Prange,

First, please accept my apologies for the significant delay in returning
revisions on this manuscript. A number of life and work priorities interfered
with a more timely response schedule and I sincerely appreciate the flexibility
*PeerJ* extends to authors. We are commited to a quick turnaround on any future
revisions or tasks associated with this manuscript and we look forward to a
final publication in *PeerJ*.

While many of the comments and suggestions from reviewers were minor, we feel
they deserved appropriate time, consideration, and exploration. We have made
several changes to the manuscript. We hope our responses here reflect that
consideration and communicate our edits. We are grateful to the reviewers for
their thoughtful comments. Lastly, we also used this opportunity to improve the
quality of the underlying telemetry data set and expand the reproducibility of
the analysis to meet or exceed expectations for open science, data availability,
and code availability.

Below, please find detailed responses to each of the reviewer comments. In
addition to this letter, the full suite of updates are all contained and
documented within two pull requests (see
<https://github.com/noaa-afsc/berchukseals-haulout/pull/51> (initial
resubmission) and <https://github.com/noaa-afsc/berchukseals-haulout/pull/52>
(additional suggestions from PeerJ staff). We have also provided a pdf document
(*\[Compare Report\] London_HauloutBehavior.pdf\]*) that indicates all changes
between the compendium supporting this revised manuscript and the compendium
supporting the originally submitted manuscript.

### 2024-08-17 analysis/paper/London_HauloutBehavior.Rmd
Squashed commit of the following:
commit cb17749e30b8733a2c326510d023904d5c2c2f35
Author: Josh M. London <josh.london@noaa.gov>
Date:   Sat Aug 17 10:37:44 2024 -0700

    Squashed commit of the following:

    commit 23f199555d6fdbd4b7d2b932ea2f7724a8ccdab6
    Author: Josh M. London <josh.london@noaa.gov>
    Date:   Sat Aug 17 10:35:18 2024 -0700

        ignore _targets.zip

commit 33f7f1920c55847a5739b37968e3ed3b9ae3f153
Author: Josh M. London <josh.london@noaa.gov>
Date:   Fri Jun 7 10:57:22 2024 -0700

    additional changes requested from staff

    - added additional link/url to the f

(ref:deployMapCaption) **Initial bio-logger deployment areas for bearded, ribbon, and spotted seals in the study between 2005 and 2020 across multiple regions within the Bering, Chukchi, and western Beaufort seas.** \linebreak Solid regions shown for each species are minimum concave polygons buffered by 60 km for enhanced visibility. The larger, shaded region indicates the spatial extent of aerial survey effort to date in the Bering, Chukchi, and Beaufort seas. Deployments were initiated across a range of months but only haul-out data from 1 March to 15 July were included in the analysis. See Figure \@ref(fig:dataMap) for the spatial distribution of observed data used in the study and Supplemental Materials \@ref(tab:deploymentTable) for additional deployment details.

@@

(ref:mapCaption) **Spatial distribution of haul-out records from 1 March through July 15 for bearded, ribbon, and spotted seal.** \linebreak Linking location estimates with haul-out records in space and time allows for inclusion of weather covariates in the final model. For this visualization, data were collated across all years between 2005 and 2020 and each hexagonal cell represents an area of 50 km^2^

@@

# pal <- c(rcartocolor::carto_pal(12,'Bold')[1:11],
#          rcartocolor::carto_pal(12,'Antique')[1:3])
pal <- c("#A6CEE3","#3385BB","#84BF96","#6DBD57","#F3E587","#F57C7C","#E42622",
         "#FBB268","#FE8D19","#DE9E83","#9D7BBA", "#977899","#7F9D55","#B15928")
names(pal) <- as.character(sort(unique(peak_ho_df$year)))

@@

This manuscript was developed as a reproducible research compendium and was
originally published as a pre-print at bioRxiv (@london2022;
https://doi.org/10.1101/2022.04.07.487572). All data used in the study and code
are available on GitHub (https://github.com/noaa-afsc/berchukseals-haulout) and
major versions archived at Zenodo (https://doi.org/10.5281/zenodo.4638221).
Original data sources for telemetry are archived as part of datasets at
the United States Animal Telemetry Network (https://portal.atn.ioos.us/), archived at Movebank (see
Movebank ID	732321226), or associated
with other published manuscripts (see supplemental material
\@ref(tab:deploymentTable)). Collated and cleaned data products needed to
replicate the analysis along with the results of all model fits are also
available and versioned as an R package on GitHub
(https://github.com/noaa-afsc/berchuksealsHauloutFits) and archived at Zenodo
(https://doi.org/10.5281/zenodo.10056308).

>>>>

(ref:deployMapCaption) **Initial bio-logger deployment areas for bearded, ribbon, and spotted seals in the study between 2005 and 2020 across multiple regions within the Bering, Chukchi, and western Beaufort seas.** \linebreak Solid regions shown for each species are minimum concave polygons buffered by 60 km for enhanced visibility. The larger, shaded region indicates the spatial extent of aerial survey effort to date in the Bering, Chukchi, and Beaufort seas. Deployments were initiated across a range of months but only haul-out data from 1 March to 15 July were included in the analysis. See Figure \@ref(fig:dataMap) for the spatial distribution of observed data used in the study and Supplemental Materials \@ref(tab:deploymentTable) for additional deployment details. World land vector data from https://naturalearthdata.com.

@@

(ref:mapCaption) **Spatial distribution of haul-out records from 1 March through July 15 for bearded, ribbon, and spotted seal.** \linebreak Linking location estimates with haul-out records in space and time allows for inclusion of weather covariates in the final model. For this visualization, data were collated across all years between 2005 and 2020 and each hexagonal cell represents an area of 50 km^2^. World land vector data from https://naturalearthdata.com.

@@

# see https://davidmathlogic.com/colorblind/#%23A6CEE3-%233385BB-%2384BF96-%23004D40-%23F3E587-%23F57C7C-%23D81B60-%23FBB268-%23FE8D19-%23DE9E83-%239D7BBA-%23977899-%237F9D55-%23B15928
# for simulation of colorblind scenarios

pal <- c("#A6CEE3","#3385BB","#84BF96","#004D40","#F3E587","#F57C7C","#D81B60",
         "#FBB268","#FE8D19","#DE9E83","#9D7BBA", "#977899","#7F9D55","#B15928")
names(pal) <- as.character(sort(unique(peak_ho_df$year)))

@@

This manuscript was developed as a reproducible research compendium and was
originally published as a pre-print at bioRxiv (@london2022;
https://doi.org/10.1101/2022.04.07.487572). All data used in the study and code
are available on GitHub (https://github.com/noaa-afsc/berchukseals-haulout) and
major versions archived at Zenodo (https://doi.org/10.5281/zenodo.4638221).
Original data sources for telemetry are archived as part of datasets at
the United States Animal Telemetry Network (https://portal.atn.ioos.us/; 
https://doi.org/10.24431/rw1k8er), archived at Movebank (see
Movebank ID	732321226), or associated
with other published manuscripts (see supplemental material
\@ref(tab:deploymentTable)). Collated and cleaned data products needed to
replicate the analysis along with the results of all model fits are also
available and versioned as an R package on GitHub
(https://github.com/noaa-afsc/berchuksealsHauloutFits) and archived at Zenodo
(https://doi.org/10.5281/zenodo.10056308).

### 2024-08-17 analysis/paper/London_HauloutBehavior.tex
Squashed commit of the following:
commit cb17749e30b8733a2c326510d023904d5c2c2f35
Author: Josh M. London <josh.london@noaa.gov>
Date:   Sat Aug 17 10:37:44 2024 -0700

    Squashed commit of the following:

    commit 23f199555d6fdbd4b7d2b932ea2f7724a8ccdab6
    Author: Josh M. London <josh.london@noaa.gov>
    Date:   Sat Aug 17 10:35:18 2024 -0700

        ignore _targets.zip

commit 33f7f1920c55847a5739b37968e3ed3b9ae3f153
Author: Josh M. London <josh.london@noaa.gov>
Date:   Fri Jun 7 10:57:22 2024 -0700

    additional changes requested from staff

    - added additional link/url to the f

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/Figure-001} \caption{\textbf{Initial bio-logger deployment areas for bearded, ribbon, and spotted seals in the study between 2005 and 2020 across multiple regions within the Bering, Chukchi, and western Beaufort seas.} \linebreak Solid regions shown for each species are minimum concave polygons buffered by 60 km for enhanced visibility. The larger, shaded region indicates the spatial extent of aerial survey effort to date in the Bering, Chukchi, and Beaufort seas. Deployments were initiated across a range of months but only haul-out data from 1 March to 15 July were included in the analysis. See Figure \ref{fig:dataMap} for the spatial distribution of observed data used in the study and Supplemental Materials \ref{tab:deploymentTable} for additional deployment details.}\label{fig:deployplot}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/Figure-003} \caption{\textbf{Spatial distribution of haul-out records from 1 March through July 15 for bearded, ribbon, and spotted seal.} \linebreak Linking location estimates with haul-out records in space and time allows for inclusion of weather covariates in the final model. For this visualization, data were collated across all years between 2005 and 2020 and each hexagonal cell represents an area of 50 km\textsuperscript{2}}\label{fig:dataMap}
\end{figure}

@@

This manuscript was developed as a reproducible research compendium and was
originally published as a pre-print at bioRxiv (London et al. (2022);
\url{https://doi.org/10.1101/2022.04.07.487572}). All data used in the study and code
are available on GitHub (\url{https://github.com/noaa-afsc/berchukseals-haulout}) and
major versions archived at Zenodo (\url{https://doi.org/10.5281/zenodo.4638221}).
Original data sources for telemetry are archived as part of datasets at
the United States Animal Telemetry Network (\url{https://portal.atn.ioos.us/}), archived at Movebank (see
Movebank ID 732321226), or associated
with other published manuscripts (see supplemental material
\ref{tab:deploymentTable}). Collated and cleaned data products needed to
replicate the analysis along with the results of all model fits are also
available and versioned as an R package on GitHub
(\url{https://github.com/noaa-afsc/berchuksealsHauloutFits}) and archived at Zenodo
(\url{https://doi.org/10.5281/zenodo.10056308}).

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/Figure-001} \caption{\textbf{Initial bio-logger deployment areas for bearded, ribbon, and spotted seals in the study between 2005 and 2020 across multiple regions within the Bering, Chukchi, and western Beaufort seas.} \linebreak Solid regions shown for each species are minimum concave polygons buffered by 60 km for enhanced visibility. The larger, shaded region indicates the spatial extent of aerial survey effort to date in the Bering, Chukchi, and Beaufort seas. Deployments were initiated across a range of months but only haul-out data from 1 March to 15 July were included in the analysis. See Figure \ref{fig:dataMap} for the spatial distribution of observed data used in the study and Supplemental Materials \ref{tab:deploymentTable} for additional deployment details. World land vector data from \url{https://naturalearthdata.com}.}\label{fig:deployplot}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/Figure-003} \caption{\textbf{Spatial distribution of haul-out records from 1 March through July 15 for bearded, ribbon, and spotted seal.} \linebreak Linking location estimates with haul-out records in space and time allows for inclusion of weather covariates in the final model. For this visualization, data were collated across all years between 2005 and 2020 and each hexagonal cell represents an area of 50 km\textsuperscript{2}. World land vector data from \url{https://naturalearthdata.com}.}\label{fig:dataMap}
\end{figure}

@@

This manuscript was developed as a reproducible research compendium and was
originally published as a pre-print at bioRxiv (London et al. (2022);
\url{https://doi.org/10.1101/2022.04.07.487572}). All data used in the study and code
are available on GitHub (\url{https://github.com/noaa-afsc/berchukseals-haulout}) and
major versions archived at Zenodo (\url{https://doi.org/10.5281/zenodo.4638221}).
Original data sources for telemetry are archived as part of datasets at
the United States Animal Telemetry Network (\url{https://portal.atn.ioos.us/};
\url{https://doi.org/10.24431/rw1k8er}), archived at Movebank (see
Movebank ID 732321226), or associated
with other published manuscripts (see supplemental material
\ref{tab:deploymentTable}). Collated and cleaned data products needed to
replicate the analysis along with the results of all model fits are also
available and versioned as an R package on GitHub
(\url{https://github.com/noaa-afsc/berchuksealsHauloutFits}) and archived at Zenodo
(\url{https://doi.org/10.5281/zenodo.10056308}).
